tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-10-01 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Save qusage

all_comparisons <- lapply(comparisons, 
                          function(comparison){
                            list_comp <- lapply(
                              list(pir_geneset,
                                   ShortLong_list,
                                   subfam_list), 
                              function(gene_list){
                                qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                                            lifeCycle_labels,
                                                            comparison,
                                                            gene_list,
                                                            n.points = 2^18)
                                list(results = qs.results.subfam, 
                                     qstable = qsTable(qs.results.subfam) %>% 
                                       mutate(contrast = qs.results.subfam$contrast))
                              })
                            names(list_comp) <- c('pir', 'shortlong', 'subfam')
                            list_comp$combined <- bind_rows(lapply(list_comp, 
                                                                   getElement, 
                                                                   'qstable'))
                            return(list_comp)
                          })
names(all_comparisons) <- comparisons

>>>>

all_comparisons <- lapply(comparisons, 
                          function(comparison){
                            list_comp <- lapply(
                              list(pir_geneset,
                                   ShortLong_list,
                                   subfam_list), 
                              function(gene_list){
                                qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                                            lifeCycle_labels,
                                                            comparison,
                                                            gene_list,
                                                            n.points = 2^18)
                                list(results = qs.results.subfam, 
                                     qstable = qsTable(qs.results.subfam) %>% 
                                       mutate(contrast = qs.results.subfam$contrast))
                              })
                            names(list_comp) <- c('pir', 'shortlong', 'subfam')
                            list_comp$combined <- bind_rows(lapply(list_comp, 
                                                                   getElement, 
                                                                   'qstable'))
                            return(list_comp)
                          })
names(all_comparisons) <- comparisons
```

```{r heatmap}
